Modularizing Street Map Generation \\ \vspace{8pt} \large An Adventure in Tensors

### 2013-12-12 paper/paper.tex
merge

\section{Existing Work}
\textit{Interactive Procedural Street Modelling} \cite{chen} introduces a novel
new concept of using tensor fields to model realistic street layouts. They 
offer
a well-defined pipeline of mathematical operations to go from simple user
inputs to a final street graph. They also implement a number of operations to
modify the street graph more granularly once it has been generated, such as
removal of roads and retracing of the roads in a defined region with a new
tensor field. The mathematical concepts fundamental to the procedural
generation algorithm are covered thoroughly and clearly.

While all of the information presented in the paper to be very well-formulated
and informative, we found the provided implementation of the described
algorithm more difficult to grasp. The large quantity of \cpp code necessary to
implement the full-featured interactive system provided by Chen et al. made it
difficult for us to thoroughly understand the constituent components such that
we would be able to modify or extend the existing code.

@@

The major eigenvectors of $t$ are
\[
    \left\{
        \lambda\mkvec{\cos{\theta}}{\sin{\theta}} ~|~ \lambda \neq 0
    \right\}
\]
The minor eigenvectors are
\[
    \left\{
        \lambda\mkvec
                {\cos{(\theta+\frac{\pi}{2})}}
                {\sin{(\theta+\frac{\pi}{2})}}
        ~|~ \lambda \neq 0
    \right\}
\]
A tensor field $T$ is a function that maps from 2D points to tensors. In the
context of this project, a tensor is simply a tool we use to determine the
direction of a field at a point. This direction is found by calculating the
eigenvectors of the tensors. Major eigenvectors are parallel to the field;
minor eigenvectors are perpendicular.

>>>>

\section{Existing Work}
\textit{Interactive Procedural Street Modelling} \cite{chen} introduces a novel
new concept of using tensor fields to model realistic street layouts. They
offer
a well-defined pipeline of mathematical operations to go from simple user
inputs to a final street graph. They also implement a number of operations to
modify the street graph more granularly once it has been generated, such as the
removal and retracing of the roads in a defined region with a new
tensor field. The mathematical concepts fundamental to the procedural
generation algorithm are covered thoroughly and clearly.

While all of the information presented in the paper completely describes all of
the necessary mathematics in a clear manner,
we found the provided implementation of the described
algorithm more difficult to grasp. The large quantity of \cpp code necessary to
implement the full-featured interactive system provided by Chen et al. made it
difficult for us to thoroughly understand the constituent components such that
we would be able to modify or extend the existing code.

@@

The major eigenvectors of $t$ are
\[
    \left\{
        \lambda\mkvec{\cos{\theta}}{\sin{\theta}} ~|~ \lambda \neq 0
    \right\}
\]
The minor eigenvectors are
\[
    \left\{
        \lambda\mkvec
                {\cos{(\theta+\frac{\pi}{2})}}
                {\sin{(\theta+\frac{\pi}{2})}}
        ~|~ \lambda \neq 0
    \right\}
\]
A tensor field $T$ describes the flow of the constraints across a field,
and is represented as a function that maps from 2D points to tensors. In the
context of this project, a tensor is simply a tool we use to determine the
direction of a field at a point. This direction is found by calculating the
eigenvectors of the tensors. Major eigenvectors are parallel to the field;
minor eigenvectors are perpendicular.
